Enabling Ambient Backscatter \\Using a Low-Cost Software Defined Radio

### 2017-05-15 introduction.tex
Added sth. to the intro and fixed a typo.

On the other hand, Software Defined Radios~(SDRs) are powerful devices, and also
have significant processing abilities. These devices offer high
sensitivity levels, as compared to the receivers employed on typical 
ambient backscatter tags. Thus, SDRs might help to
significantly improve the communication range, and also coverage 
area to receive ambient backscatter transmissions.

>>>>

On the other hand, Software Defined Radios~(SDRs) are powerful devices, and also
have significant processing abilities. These devices offer high
sensitivity levels, as compared to the receivers employed on typical 
ambient backscatter tags. Thus, SDRs might help to
significantly improve the communication range, and also coverage 
area to receive ambient backscatter transmissions. Moreover the I/Q demodulator ICs, which represent the heart of an SDR system are very cheap as they are used a lot in digital communication. We are confident to be able to accelerate the research in the backscattering field, since we introduce a backscattering equipement, which is easily affordable by any student.
